FoRTE baseline

### 2019-09-10 analysis/paper/paper.Rmd
Use bold face for letters in Figure 4 results text

Model structure and parameters interacted to determine the community assembly and dynamics of each simulation, with consequences for overall ecosystem productivity that varied by model structure (Figure 4).
Consider simulations _A_ and _C_, the former showing competition of early hardwood with pine, and the latter completely dominated by pine:
With a closed canopy and static traits, both simulations produced similar overall LAI and NPP values (Figure 3), but moving to a finite canopy dramatically increased the total LAI in _C_ without much affecting _A_, while enabling trait plasticity dramatically increased the NPP of _A_ without much affecting _C_ (Figure 3).
This example also shows the impacts of different configurations on predicted community dynamics -- namely, in this specific case, enabling trait plasticity helped pine out-perform early hardwood, but only under a closed (rather than finite) canopy.
Finite canopy radius similarly benefits early hardwood in its competition against late hardwood in simulations _B_ and, to a lesser extent, _D_.
Simulations _B_ and _D_ also show that the sensitivity of a given parameter combination to model structure is itself dependent on the parameters -- simulation _B_ produced similar ecological dynamics and aggregate state variables regardless of model configuration (except the extreme cases; Figure 3), while simulation _D_ had near-zero NPP and LAI in two cases (closed, two-stream, static and finite, multi-scatter, plastic), comparable NPP and LAI to _B_ with closed canopy and trait plasticity, and higher NPP and LAI than _D_ with a finite canopy, multi-scatter radiative transfer, and static traits (Figure 3).

>>>>

Model structure and parameters interacted to determine the community assembly and dynamics of each simulation, with consequences for overall ecosystem productivity that varied by model structure (Figure 4).
Consider simulations **A** and **C**, the former showing competition of early hardwood with pine, and the latter completely dominated by pine:
With a closed canopy and static traits, both simulations produced similar overall LAI and NPP values (Figure 3), but moving to a finite canopy dramatically increased the total LAI in **C** without much affecting **A**, while enabling trait plasticity dramatically increased the NPP of **A** without much affecting **C** (Figure 3).
This example also shows the impacts of different configurations on predicted community dynamics -- namely, in this specific case, enabling trait plasticity helped pine out-perform early hardwood, but only under a closed (rather than finite) canopy.
Finite canopy radius similarly benefits early hardwood in its competition against late hardwood in simulations **B** and, to a lesser extent, **D**.
Simulations **B** and **D** also show that the sensitivity of a given parameter combination to model structure is itself dependent on the parameters -- simulation **B** produced similar ecological dynamics and aggregate state variables regardless of model configuration (except the extreme cases; Figure 3), while simulation **D** had near-zero NPP and LAI in two cases (closed, two-stream, static and finite, multi-scatter, plastic), comparable NPP and LAI to **B** with closed canopy and trait plasticity, and higher NPP and LAI than **D** with a finite canopy, multi-scatter radiative transfer, and static traits (Figure 3).
